---
title: "Assignment 4"
author: "Oyvind Nordgard"
date: "25 november 2018"
output: html_document
---


```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE, message=FALSE} 

library(rvest)
library(tidyverse)
library(rlist)
library(plyr)  
```

# **Web Scraping**

Specifying the url for desired website to be scrapped
```{r}
url <- "https://w2.brreg.no/kunngjoring/kombisok.jsp?datoFra=01.10.2017&datoTil=30.09.2018&id_region=100&id_fylke=19&id_kommune=1902&id_niva1=51&id_niva2=-+-+-&id_bransje1=0"

```

Reading & checking the HTML code from the website
```{r}
Webpage <- read_html(url)
str(Webpage)
```

Using CSS selectors to scrap the kunngjorings section
```{r}
Kunngjorings_Type_html <- html_nodes(Webpage,"p a")
```

Converting the title of the data to text
```{r}
Announcement <- html_text(Kunngjorings_Type_html)
Announcement <- factor(Announcement)
head(Announcement)
tail(Announcement)
str(Announcement)
```


Using CSS selectors to scrap the dato section and converting it to text,
and converting dato from character to date format. 

```{r}
dato1 <- html_nodes(Webpage,"tr~ tr+ tr td:nth-child(6) p")
dato <- html_text(dato1)
head(dato)
dato <- as.Date(dato, format = "%d.%m.%Y")
str(dato)
```

Using CSS selectors to scrap the digits section, then converting it to text
```{r}
digits_html<-html_nodes(Webpage,"td:nth-child(4) p")
digits <- html_text(digits_html)
head(digits)
str(digits)
```
Preparing the data, removing extra space in the digits
```{r}
digits <- str_replace_all(string= digits, pattern=" ", repl="")
```

Converting from character to numeric
```{r}
digits <- as.numeric(digits)
str(digits)
head(digits)
```


Using CSS selectors to scrap the names section, and converting the html
to text and characters.

```{r}
name_html_type<-html_nodes(Webpage,"td td:nth-child(2) p")
name <-html_text(name_html_type[1:162])
name <-as.character(name)
str(name)
```



Creating a dataframe from the vectors

```{r}
dataframe <- data.frame(name, dato, digits, Announcement, stringsAsFactors = F)
glimpse(dataframe)
dataframe <- filter(dataframe, digits > 1000000)
dim(dataframe)
```
Selecting companies (i.e. "AS")
```{r}
Bedrift_Announcement<-dataframe[grep("AS", dataframe$name),]
str(Bedrift_Announcement)
head(Bedrift_Announcement)

```


Companies who have been declared compulsory dissoluted.
```{r}
Compulsory_disolved<-Bedrift_Announcement[grep("Tvangsoppløsning", Bedrift_Announcement$Announcement),]
names(Compulsory_disolved)
str(Compulsory_disolved)
head(Compulsory_disolved)
```

Plotting announcement and date.
```{r}
qplot(data = Bedrift_Announcement,dato,fill = Announcement, binwidth = 50)
```

Frequency of announcements
```{r}
count(count(Bedrift_Announcement,"Bedrift_Announcement$Announcement"))
```

```{r}
count(Bedrift_Announcement,"Bedrift_Announcement$Announcement")
```

